Evaluating the Capabilities of the Lattice Boltzmann Method for non-Newtonian and Free-surface Flow towards Applications in Wellbore Cementing

### 2018-02-12 response-to-reviewers.tex

\begin{document}

	\pagenumbering{gobble}

\section*{Response to reviewers}

Thank you very much for your assistance in reviewing this paper. We are sure that with your help, this has become a much better work. We hope that the attached edited copy of ``Numerical Investigation of the Accuracy, Stability, and Efficiency of Lattice Boltzmann Methods in Simulating Non-Newtonian Flow'' will answer any questions previously raised, and will be satisfactory for publication.
The response is followed by a copy of the manuscript with marked up changes for the convenience of any reviewer interested in seeing such a copy.

@@

	\item \emph{Page 15: An exemplary figure (e.g. for $\tau_y = 4.0*10^-5$) comparing the viscosity
		according to the exact Bingham relationship and the approximations according to
		Papanastasiou with $m=10^5$ and $m=10^8$, respectively, would allow a comparison at
		first glance. Also the reader could see differences directly.}

	This figure was added.
	Thank you for the suggestion.

	\item \emph{Page 22: Why don’t you compare the MRT calculations to the BGK,
		$m=10^8$, cases, since $m=10^8$ was used for MRT as well?}

	This is a good point.
	The discussion has been expanded to compare the MRT calculations to the BGK, $m = 10^8$ cases.
